A Survey of Web Testing Frameworks and Workflow for Testing JavaScript Applications

### 2014-05-31 Paper/paper.tex
Redid figures so they're where I want them, minor 'typo' tweaks

% Two Column Format
\documentclass[12pt]{ucthesis}
%this allows us to specify sections to be single or multi column so that things like title page and table of contents are single column
\usepackage{listings}
\usepackage[disable]{todonotes}
\usepackage{url}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[letterpaper]{geometry}
\usepackage[overload]{textcase}
\usepackage{verbatim}

@@

\lstdefinelanguage{JavaScript}{
  keywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break},
  keywordstyle=\color{blue}\bfseries,
  ndkeywords={class, export, boolean, throw, implements, import, this},
  ndkeywordstyle=\color{darkgray}\bfseries,
  identifierstyle=\color{black},
  sensitive=false,
  comment=[l]{//},
  morecomment=[s]{/*}{*/},
  commentstyle=\color{purple}\ttfamily,
  stringstyle=\color{red}\ttfamily,
  morestring=[b]',
  morestring=[b]"
}

\lstset{frame=tb,
  language=JavaScript,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true
  tabsize=3
}

@@

% Different font in captions (single-spaced, bold) ------------
\newcommand{\captionfonts
\captionfonts}{\small\bf\ssp}

\makeatletter  % Allow the use of @ in command names
\long\def\@makecaption#1#2{%
  \vskip\abovecaptionskip
  \sbox\@tempboxa{{\captionfonts
\captionfonts #1: #2}}%
  \ifdim \wd\@tempboxa >\hsize
    {\captionfonts
\captionfonts #1: #2\par}
  \else
    \hbox to\hsize{\hfil\box\@tempboxa\hfil}%
  \fi
  \vskip\belowcaptionskip}
\makeatother   % Cancel the effect of \makeatletter
% ---------------------------------------

@@

\begin{figure}
	\begin{center}
	\includegraphics[width=0.75\linewidth]{defectcost.jpg} 
	\captionfonts
\caption[figure]{Illustration relating phase bug found in with effort required to fix.}
\end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.75\linewidth]{todo_home.png}
  \captionfonts
\caption[todo]{ToDo app home page, simple three-button naviagation}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.75\linewidth]{todo_some_tasks.png}
  \captionfonts
\caption[figure]{ToDo app task page}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.75\linewidth]{todo_completed.png}
  \captionfonts
\caption[figure]{ToDo app completed tasks page}
\end{center}
\end{figure}

@@

Mocha, by default, also uses the \lstinline{describe -> it(\"should...\"} pattern to create tests. Mocha offers a variety of other test interfaces for developer's to write their test code as well as a custom, nearly unstructured variety. A few of the testing interfaces are outlined here:
\begin{lstlisting}
// BDD (default)
describe('BDD Suite', function () {
  it('should be test 1', function () {
    ...
  });
});

@@

\subsubsection{Assertion Library of Choice: Chai.js \cite{Chaijs}}
For the assertion library we chose Chai.js.  It offers the most flexibility for writing assertions that we'd found. It provides access to an Expect API, a Should API, and a more general Assert API. The Expect API provides assertions in the form of \lstinline{expect(myVar).to.equal(10);} or \lstinline{expect(myArr).to.have.length(10);}. The Should API has assertions of the form \lstinline{myVar.should.be.a(\'number\');} or \lstinline{myArr.should.have.length(10);}. Finally, the Assert API has the more tried and true \lstinline{assert.equal(myVar, 10);} and \lstinline{assert.lengthOf(myArr, 10);}. The various APIs combined with Mocha's flexibility led to a nice developer experience that can appeal to a variety of different developers.

\subsection{QUnit \cite{QUnit}}
QUnit is an Assertion style framework developed by the jQuery Foundation, the makers of jQuery, an immensely popular framework for DOM manipulation and access. QUnit is a bit more developer-centered and not as ``feel-good'' as the other frameworks but has, so far, been the most easy to use and has the most thorough test reporting of any framework out of the box. Mocha and Jasmine show how many ``specs'', the \lstinline{it} functions, have passed, which is great information, but QUnit takes it a step further and breaks down each spec into the asserts contained within:
\begin{figure}
  \begin{center}
  \includegraphics[width=\linewidth]{qunitrunner.png} 
  \captionfonts
\caption[figure]{Each individual spec is further broken down into the assertions within it.}
\end{center}
\end{figure}
An interesting feature that QUnit has that we'd not seen elsewhere is the ability to specify how many assertions are expected to run in the test. This is incredibly useful for callbacks. By setting an expected number of assertions, tests can no longer fail silently just because an assertion was never run. If the QUnit test finishes and the assertion count is not what was specified, it will fail the test and let the developer know fewer assertions were called than expected.

@@

Jenkins is a series of web pages that are set up to run on a given server. This is what it looks like:
\begin{figure}
  \begin{center}
  \includegraphics[width=0.95\linewidth]{jenkins.png}
\end{center}
\end{figure}
Most companies give Jenkins a sub-domain on their web pages.

@@

We decided to install everything globally because it made writing our scripts easier, but it's not a requirement. Everything can be done with locally installed node modules. Instead of using the command by itself, the developer would just need to supply the full path to the executable, which is generally \lstinline{PATH\_TO\_REPO/node\_modules/MODULE\_NAME/bin/MODULE\_NAME} or something similar.

@@

To get Chai running with Mocha, just \lstinline{require(...)} the appropriate chai assertion method in the test and start writing. For example, to get the Assert library: \lstinline{var assert = require(\'chai\').assert;}

@@

Here is the new project page:
\begin{figure}
  \begin{center}
  \includegraphics[width=0.95\linewidth]{magnumCI_new_project.png}
\end{center}
\end{figure}

Fill out the fields with the appropriate values for a given project and click ``Create Project''. Depending on what the setup is for your project, you'll see slightly varying web pages after you create your project. One thing in common, though, is the button at the bottom of the steps list that says ``Customize Build''. After following the instructions, click ``Customize Build'':
\begin{figure}
  \begin{center}
  \includegraphics[width=0.95\linewidth]{magnumCI_customize_build.png}
\end{center}
\end{figure}
There are a number of configuration options and panes that can be accessed on the left side. Our focus was making sure the ``Build Configuration'' tab was properly set up. This involved selecting the correct branch, the correct Node.js runtime version, the correct database from the ``Resources'' area, and adding the appropriate commands in the build steps. In our case we wanted ``mongoDB'' and ``Xvfb'' for UI testing, and then \lstinline{npm install -g} in the ``Dependencies Installation'' to make sure our modules are available when we need them. Finally, we run Nightwatch using \lstinline{nightwatch -c nightwatch.json} (the nightwatch flags will be outlined in the next section) in the ``Test suite commands'' box. All of that makes our build configuration page look like this:
\begin{figure}
  \begin{center}
  \includegraphics[width=0.95\linewidth]{magnumCI_customize_build_filled.png}
\end{center}
\end{figure}
After that setup, our project is ready to go. Anytime we commit from then on, MagnumCI will run and notify us of successful and unsuccessful builds.

@@

The configuration file has plenty of options to get Nightwatch to do exactly what the developer wants, some of the more important ones include the \lstinline{selenium} object that holds information about where the executable is located and what ports to run on, the \lstinline{src\_folders} attribute to specify a source directory, and the \lstinline{test\_settings} object that contains configurations for default web pages, differing environments, and some desired capabilities.

To run Nightwatch, navigate to the project folder and run \lstinline{nightwatch -c path\_to\_nightwatch\_config}. This will use the \lstinline{src\_folders} attribute to determine where to look for the tests, start the Selenium server, and run the tests. When debugging certain functions of even test cases, tests can be isolated with the \lstinline{-t} flag: \lstinline{nightwatch -c nightwatch.json -t folder1/test1.js}. Nightwatch offers a number of other command-line arguments that are available on their developer guide. \cite{NightwatchJS}

@@

\section{PolyXpress Player Screenshots}
\begin{figure}
  \begin{center}
  \includegraphics[width=0.65\linewidth]{px_stories.png}
  \captionfonts
\caption[figure]{Story selection}
\end{center}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.65\linewidth]{px_chapter_pane.png}
  \captionfonts
\caption[figure]{Chapter pane with approximate distances to each chapter}
\end{center}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.65\linewidth]{px_chap_instructions.png}
  \captionfonts
\caption[figure]{Each page and element of PolyXpress has instructions, here they are for Chapters}
\end{center}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.65\linewidth]{px_chapter_locs.png}
  \captionfonts
\caption[figure]{A map of the chapter location in relation to the player}
\end{center}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.65\linewidth]{px_marketplace.png}
  \captionfonts
\caption[figure]{PolyXpress marketplace, to find other published stories}
\end{center}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.65\linewidth]{px_player_loc.png}
  \captionfonts
\caption[figure]{A map centered around the player}
\end{center}
\end{figure}

\section{PolyXpress Author Screenshots}
\begin{figure}
  \begin{center}
  \includegraphics[width=0.65\linewidth]{px_author_home.png}
  \captionfonts
\caption[figure]{PolyXpress Authoring Tool}
\end{center}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.65\linewidth]{px_create_event.png}
  \captionfonts
\caption[figure]{Form to create an Event}
\end{center}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.65\linewidth]{px_create_event2.png}
  \captionfonts
\caption[figure]{Bottom of form to create an Event}
\end{center}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.65\linewidth]{px_create_chap.png}
  \captionfonts
\caption[figure]{Form for creating Chapters}
\end{center}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.65\linewidth]{px_create_chap2.png}
  \captionfonts
\caption[figure]{Events are selected manually for inclusion in Chapters}
\end{center}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.65\linewidth]{px_create_story.png}
  \captionfonts
\caption[figure]{Story creation asks if the user wants their story published}
\end{center}
\end{figure}

>>>>

% Two Column Format
\documentclass[12pt]{ucthesis}
%this allows us to specify sections to be single or multi column so that things like title page and table of contents are single column
\usepackage{listings}
\usepackage{caption}
\usepackage[disable]{todonotes}
\usepackage{url}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[letterpaper]{geometry}
\usepackage[overload]{textcase}
\usepackage{verbatim}

@@

\lstdefinelanguage{JavaScript}{
  keywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break, this},
  keywordstyle=\color{blue}\bfseries,
  ndkeywords={class, export, boolean, throw, implements, import, this},
  ndkeywordstyle=\color{darkgray}\bfseries,
  identifierstyle=\color{black},
  sensitive=false,
  comment=[l]{//},
  morecomment=[s]{/*}{*/},
  commentstyle=\color{purple}\ttfamily,
  stringstyle=\color{red}\ttfamily,
  morestring=[b]',
  morestring=[b]"
}

\lstset{frame=tb,
  language=JavaScript,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}

\newenvironment{Figure}
  {\par\medskip\noindent\minipage{\linewidth}}
  {\endminipage\par\medskip}

@@

% Different font in captions (single-spaced, bold) ------------
\newcommand{\captionfonts}{\small\bf\ssp}

\makeatletter  % Allow the use of @ in command names
\long\def\@makecaption#1#2{%
  \vskip\abovecaptionskip
  \sbox\@tempboxa{{\captionfonts #1: #2}}%
  \ifdim \wd\@tempboxa >\hsize
    {\captionfonts #1: #2\par}
  \else
    \hbox to\hsize{\hfil\box\@tempboxa\hfil}%
  \fi
  \vskip\belowcaptionskip}
\makeatother   % Cancel the effect of \makeatletter
% ---------------------------------------

@@

\begin{Figure}
  \centering
	\includegraphics[width=0.75\linewidth]{defectcost.jpg} 
	\captionof{figure}{Illustration relating phase bug found in with effort required to fix.}
\end{Figure}

@@

\begin{Figure}
  \centering
  \includegraphics[width=0.75\linewidth]{todo_home.png}

\captionof{figure}{ToDo app home page, simple three-button naviagation}

\end{Figure}

\begin{Figure}
  \centering
  \includegraphics[width=0.75\linewidth]{todo_some_tasks.png}

\captionof{figure}{ToDo app task page}

\end{Figure}

\begin{Figure}
  \centering
  \includegraphics[width=0.75\linewidth]{todo_completed.png}

\captionof{figure}{ToDo app completed tasks page}

\end{Figure}

@@

Mocha, by default, also uses the \lstinline{describe -> it("should..."} pattern to create tests. Mocha offers a variety of other test interfaces for developer's to write their test code as well as a custom, nearly unstructured variety. A few of the testing interfaces are outlined here:
\begin{lstlisting}
// BDD (default)
describe('BDD Suite', function () {
  it('should be test 1', function () {
    ...
  });
});

@@

\subsubsection{Assertion Library of Choice: Chai.js \cite{Chaijs}}
For the assertion library we chose Chai.js.  It offers the most flexibility for writing assertions that we'd found. It provides access to an Expect API, a Should API, and a more general Assert API. The Expect API provides assertions in the form of \lstinline{expect(myVar).to.equal(10);} or \lstinline{expect(myArr).to.have.length(10);}. The Should API has assertions of the form \lstinline{myVar.should.be.a('number');} or \lstinline{myArr.should.have.length(10);}. Finally, the Assert API has the more tried and true \lstinline{assert.equal(myVar, 10);} and \lstinline{assert.lengthOf(myArr, 10);}. The various APIs combined with Mocha's flexibility led to a nice developer experience that can appeal to a variety of different developers.

\subsection{QUnit \cite{QUnit}}
QUnit is an Assertion style framework developed by the jQuery Foundation, the makers of jQuery, an immensely popular framework for DOM manipulation and access. QUnit is a bit more developer-centered and not as ``feel-good'' as the other frameworks but has, so far, been the most easy to use and has the most thorough test reporting of any framework out of the box. Mocha and Jasmine show how many ``specs'', the \lstinline{it} functions, have passed, which is great information, but QUnit takes it a step further and breaks down each spec into the asserts contained within:
\begin{Figure}
  \centering
  \includegraphics[width=\linewidth]{qunitrunner.png}

\captionof{figure}{Each individual spec is further broken down into the assertions within it.}

\end{Figure}
An interesting feature that QUnit has that we'd not seen elsewhere is the ability to specify how many assertions are expected to run in the test. This is incredibly useful for callbacks. By setting an expected number of assertions, tests can no longer fail silently just because an assertion was never run. If the QUnit test finishes and the assertion count is not what was specified, it will fail the test and let the developer know fewer assertions were called than expected.

@@

Jenkins is a series of web pages that are set up to run on a given server. This is what it looks like:
\begin{Figure}[!ht]
  \centering
  \includegraphics[width=0.95\linewidth]{jenkins.png}

\end{Figure}
Most companies give Jenkins a sub-domain on their web pages.

@@

We decided to install everything globally because it made writing our scripts easier, but it's not a requirement. Everything can be done with locally installed node modules. Instead of using the command by itself, the developer would just need to supply the full path to the executable, which is generally \lstinline{PATH_TO_REPO/node_modules/MODULE_NAME/bin/MODULE_NAME} or something similar.

@@

To get Chai running with Mocha, just \lstinline{require(...)} the appropriate chai assertion method in the test and start writing. For example, to get the Assert library: \lstinline{var assert = require('chai').assert;}

@@

Here is the new project page:
\begin{Figure}
  \centering
  \includegraphics[width=0.95\linewidth]{magnumCI_new_project.png}

\end{Figure}

Fill out the fields with the appropriate values for a given project and click ``Create Project''. Depending on what the setup is for your project, you'll see slightly varying web pages after you create your project. One thing in common, though, is the button at the bottom of the steps list that says ``Customize Build''. After following the instructions, click ``Customize Build'':
\begin{Figure}
  \centering
  \includegraphics[width=0.95\linewidth]{magnumCI_customize_build.png}

\end{Figure}
There are a number of configuration options and panes that can be accessed on the left side. Our focus was making sure the ``Build Configuration'' tab was properly set up. This involved selecting the correct branch, the correct Node.js runtime version, the correct database from the ``Resources'' area, and adding the appropriate commands in the build steps. In our case we wanted ``mongoDB'' and ``Xvfb'' for UI testing, and then \lstinline{npm install -g} in the ``Dependencies Installation'' to make sure our modules are available when we need them. Finally, we run Nightwatch using \lstinline{nightwatch -c nightwatch.json} (the nightwatch flags will be outlined in the next section) in the ``Test suite commands'' box. All of that makes our build configuration page look like this:
\begin{Figure}
  \centering
  \includegraphics[width=0.95\linewidth]{magnumCI_customize_build_filled.png}

\end{Figure}
After that setup, our project is ready to go. Anytime we commit from then on, MagnumCI will run and notify us of successful and unsuccessful builds.

@@

The configuration file has plenty of options to get Nightwatch to do exactly what the developer wants, some of the more important ones include the \lstinline{selenium} object that holds information about where the executable is located and what ports to run on, the \lstinline{src_folders} attribute to specify a source directory, and the \lstinline{test_settings} object that contains configurations for default web pages, differing environments, and some desired capabilities.

To run Nightwatch, navigate to the project folder and run \lstinline{nightwatch -c path_to_nightwatch_config}. This will use the \lstinline{src_folders} attribute to determine where to look for the tests, start the Selenium server, and run the tests. When debugging certain functions of even test cases, tests can be isolated with the \lstinline{-t} flag: \lstinline{nightwatch -c nightwatch.json -t folder1/test1.js}. Nightwatch offers a number of other command-line arguments that are available on their developer guide. \cite{NightwatchJS}

@@

\section{PolyXpress Player Screenshots}
\begin{Figure}
  \centering
  \includegraphics[width=0.65\linewidth]{px_stories.png}

\captionof{figure}{Story selection}

\end{Figure}

\begin{Figure}
  \centering
  \includegraphics[width=0.65\linewidth]{px_chapter_pane.png}

\captionof{figure}{Chapter pane with approximate distances to each chapter}

\end{Figure}

\begin{Figure}
  \centering
  \includegraphics[width=0.65\linewidth]{px_chap_instructions.png}

\captionof{figure}{Each page and element of PolyXpress has instructions, here they are for Chapters}

\end{Figure}

\begin{Figure}
  \centering
  \includegraphics[width=0.65\linewidth]{px_chapter_locs.png}

\captionof{figure}{A map of the chapter location in relation to the player}

\end{Figure}

\begin{Figure}
  \centering
  \includegraphics[width=0.65\linewidth]{px_marketplace.png}

\captionof{figure}{PolyXpress marketplace, to find other published stories}

\end{Figure}

\begin{Figure}
  \centering
  \includegraphics[width=0.65\linewidth]{px_player_loc.png}

\captionof{figure}{A map centered around the player}

\end{Figure}

\section{PolyXpress Author Screenshots}
\begin{Figure}
  \centering
  \includegraphics[width=0.65\linewidth]{px_author_home.png}

\captionof{figure}{PolyXpress Authoring Tool}

\end{Figure}

\begin{Figure}
  \centering
  \includegraphics[width=0.65\linewidth]{px_create_event.png}

\captionof{figure}{Form to create an Event}

\end{Figure}

\begin{Figure}
  \centering
  \includegraphics[width=0.65\linewidth]{px_create_event2.png}

\captionof{figure}{Bottom of form to create an Event}

\end{Figure}

\begin{Figure}
  \centering
  \includegraphics[width=0.65\linewidth]{px_create_chap.png}

\captionof{figure}{Form for creating Chapters}

\end{Figure}

\begin{Figure}
  \centering
  \includegraphics[width=0.65\linewidth]{px_create_chap2.png}

\captionof{figure}{Events are selected manually for inclusion in Chapters}

\end{Figure}

\begin{Figure}
  \centering
  \includegraphics[width=0.65\linewidth]{px_create_story.png}

\captionof{figure}{Story creation asks if the user wants their story published}

\end{Figure}
